Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
rm spatsoc
minor edits

```{r pkgs}
library(spatsoc)
library(data.table)
```

@@

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond2016],
to avoid predators [@Bergerud1985], and access islands during calving
[@Bergerud1990]. Even for adept swimmers like caribou, that have hollow hair
shafts to presumably aid in flotation, the energetic expenditure of swimming for
quadrupedal mammals is significantly higher than walking or running, and
drowning is also possible [@Miller1985]. Despite the abundance of coastal and
island caribou herds, only a handful of examples have documented caribou
swimming in the ocean [e.g. @Miller1995; @Miller2002;
@Jeffery2007; @Ricca2012]. Caribou may swim between islands in the ocean for
similar reasons they swim in freshwater [@Leblond2016], mainly concerning
predator avoidance or movement between habitats. We propose that one such
explanation, the forage limitation hypothesis, is the most likely explanation
for oceanic swimming for caribou that live on islands in the Fogo Island
archipelago.

>>>>

```{r pkgs}
library(data.table)
```

@@

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond2016],
to avoid predators [@Bergerud1985], and to access islands during calving
[@Bergerud1990]. Even for adept swimmers like caribou, that have hollow hair
shafts that aid in flotation, the energetic expenditure of swimming for
quadrupedal mammals is significantly higher than walking or running, and
drowning is also possible [@Miller1985]. Despite the abundance of coastal and
island caribou herds, only a handful of examples have documented caribou
swimming in the ocean [e.g. @Miller1995; @Miller2002;
@Jeffery2007; @Ricca2012]. Caribou may swim between islands in the ocean for
similar reasons they swim in freshwater [@Leblond2016], mainly concerning
predator avoidance or movement between habitats. We propose that one such
explanation, the forage limitation hypothesis, is the most likely explanation
for oceanic swimming for caribou that live on islands in the Fogo Island
archipelago.
